% Configuration
\input{includes/config.tex}
\input{includes/pandoc.tex}

\addbibresource{bibliography/references.bib}
%
\begin{document}
%
% Titlepage
\maketitle{Bachelor's Thesis}{Software Systems Science}{Migrating an Open Source Application to the Java 9 Module System}{Florian Beetz}{\today}
%
% TOCs
\pagenumbering{Roman}
\tableofcontents
\newpage
\fancyhead[LO]{\footnotesize\sc\nouppercase{\leftmark}}
\setcounter{page}{1}
\pagenumbering{arabic}
%
% Insert your chapters here
%
\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

\hypertarget{background}{%
\section{Background}\label{background}}

\hypertarget{java-programming-language}{%
\subsection{Java Programming Language}\label{java-programming-language}}

The Java programming language was developed by Sun Microsystems under
the name Oak in 1991 \autocite{Oracle2015}. Oak was designed to be
processor-independent and should be used in consumer electronics. In
1992 the industry had little interest in Oak, so the developers switched
to bringing the language to the internet. The WebRunner browser was
released in 1994, being the first browser supporting moving objects and
dynamic executable content. Due to trademark issues Oak was renamed to
Java in 1995. In the same year the developers of the Netscape Navigator
browser announced that they will include Java support. The first version
of Java was then released in 1996.

\hypertarget{jabref-bibliography-manager}{%
\subsection{JabRef Bibliography
Manager}\label{jabref-bibliography-manager}}

JabRef is an open source bibliography reference manager using the
standard LaTeX bibliography format BibTex as its native file format. The
project is hosted on GitHub\footnote{https://github.com/JabRef/jabref}
and currently has over 200 contributors and around 140,000 lines of Java
code.
\newpage

%\addcontentsline{toc}{chapter}{Appendix}

\printbibliography[heading=bibintoc]

\end{document}
